### 2017-05-30 sheets/basis-3/sheet-basis-3.tex
Update exercise 3.6

\begin{answer}
  In the following we will consider a representation of the permutation as a
  tuple of two elements $(a, b)$, where $a \mapsto b$ is an element of a
  bijection.
  \begin{itemize}
    \item[(a)]
      For any $A \in ob(\cat{B}), C \in ob(\Set), f: A \to C$
      \begin{align*}
        \Sym(f) &= \lambda (a, b). (f(a), f(b))\\
        \Ord(f) &= \lambda (a, b).(f(a), f(b))
      \end{align*}
    \item[(b)]
      Let's fix a finite set $A$ and define $\Sym \to \Ord$ on it.\\
      \begin{align*}
        A &= \{a, b\}\\
        \Sym(A) &= \{\{(a, a), (b, b)\}, \{(a, b), (b, a)\}\}\\
        \Ord(A) &= \{\{(a, b), (a, a), (b, b)\}, \{(b, a), (a, a), (b, b)\}\},\\
      \end{align*}
      Natural transformation $\alpha: \Sym(A) \to \Ord(A)$:\\
      \begin{align*}
        \alpha_A(\{(a, a), (b, b)\}) &= \{(a, b), (a, a), (b, b)\}\\
        \alpha_A(\{(a, b), (b, a)\}) &= \{(b, a), (a, a), (b, b)\}
      \end{align*}
      And a permutation of $A$:
      \begin{align*}
        f(a) &= b\\
        f(b) &= a
      \end{align*}
      Now, for $\alpha$ to indeed be a natural transformation, the  naturality
      axiom should hold for all arrows $A \to A$, including $f$. Let's check if
      it holds by applying $f$.\\
      \begin{align*}
        &\alpha_A(f(\{(a, a), (b, b)\})) &= \alpha_A(\{(b, b), (a, a)\}) =&& \{(b, a), (b, b), (a, a)\}\\
        &\alpha_A(f(\{(a, b), (b, a)\})) &= \alpha_A(\{(b, a), (a, b)\}) =&& \{(a, b), (b, b), (a, a)\}
      \end{align*}
      Here $\alpha_A$ contradicts our definition of it and we can conclude that
      it is not a natural transformation. The only other possibility of
      defining $\alpha_A$ would be to switch the images of sets in the
      definition, but the applying $f$ will yield us a similar contradictory
      result.  From this we see that no matter how we define $\alpha_A$, the
      naturality axiom will not hold for our $f$, hence we cannot have a
      natural transformation for $\Sym(A) \to \Ord(A)$ and, in general, a
      natural transformation $\Sym \to \Ord$.
    \item[(c)]
      From combinatorics we know that the number of all permutations of a
      finite set of size $n$ is exactly $n$!:\\
      \begin{equation*}
        |\Sym(X)| = n!
      \end{equation*}
      We can also notice that we may consider permutations as an order too,
      hence the number of all orders is:
      \begin{equation*}
        |\Ord(X)| = n!
      \end{equation*}
  \end{itemize}
  So we know that $\Sym$ and $\Ord$ have exactly the same number of elements
  and generally we can come up with a mapping between those elements, such that
  $\Sym(X) \iso \Ord(X)$ for all $X \in \cat{B}$. However, we have also shown
  that we cannot define a natural transformation $\Sym \to \Ord$ which gives
  that there's no natural isomorphism between those categories.
\end{answer}

@@

                    %TODO

>>>>

\begin{answer}
  In the following we will consider a graph representation of the permutation
  function which is a tuple of two elements $(a, b)$, where $a \mapsto b$ is an
  element of a bijection.
  \begin{itemize}
    \item[(a)]
      For any $A \in ob(\cat{B}), C \in ob(\Set), f: A \to C$
      \begin{align*}
        \Sym(f) &= \lambda X. \{(f(a), f(b)) | (a, b) \in X \}\\
        \Ord(f) &= \lambda X. \{(f(a), f(b)) | (a, b) \in X \}\\
      \end{align*}
    \item[(b)]
      Let's fix a finite set $A$ and try to define $\Sym \to \Ord$ on it.\\
      \begin{align*}
        A &= \{a, b\}\\
        \Sym(A) &= \{\{(a, a), (b, b)\}, \{(a, b), (b, a)\}\}\\
        \Ord(A) &= \{\{(a, b), (a, a), (b, b)\}, \{(b, a), (a, a), (b, b)\}\},\\
      \end{align*}
      Natural transformation $\alpha_A: \Sym(A) \to \Ord(A)$:\\
      \begin{align*}
        \alpha_A(\{(a, a), (b, b)\}) &= \{(a, b), (a, a), (b, b)\}\\
        \alpha_A(\{(a, b), (b, a)\}) &= \{(b, a), (a, a), (b, b)\}
      \end{align*}
      And a permutation of $A$:
      \begin{align*}
        f(a) &= b\\
        f(b) &= a
      \end{align*}
      Now, for $\alpha$ to indeed be a natural transformation, the  naturality
      axiom should hold for all arrows $A \to A$, including $f$. Let's check if
      it holds by applying $f$.\\
      \begin{align*}
        &\alpha_A(f(\{(a, a), (b, b)\})) &= \alpha_A(\{(b, b), (a, a)\}) =&& \{(b, a), (b, b), (a, a)\}\\
        &\alpha_A(f(\{(a, b), (b, a)\})) &= \alpha_A(\{(b, a), (a, b)\}) =&& \{(a, b), (b, b), (a, a)\}
      \end{align*}
      Here we get a contradiction with the definition of $\alpha_A$ and we can
      therefore conclude that it is not a natural transformation (naturality
      axiom doesn't hold). The only other possibility of defining $\alpha_A$
      (we can define this natural transformation in only two ways, as there are
      only two arrows possible between $\Sym(A)$ and $\Ord(A)$ in $\Set$) would
      be to swap the images in the definition of $\alpha_A$, but the
      application of $f$ will yield us a similar contradictory result. From
      this we see that no matter how we define $\alpha_A$, the naturality axiom
      will not hold for our $f$, hence we cannot have a natural transformation
      for $\Sym(A) \to \Ord(A)$ and, since in general we need the naturality
      axiom to hold for all objects and arrows between them, a natural
      transformation $\Sym \to \Ord$.
    \item[(c)]
      From combinatorics we know that the number of all permutations of a
      finite set of size $n$ is exactly $n$!:\\
      \begin{equation*}
        |\Sym(X)| = n!
      \end{equation*}
      We can also notice that we may consider permutations as an order too,
      hence the number of all orders is:
      \begin{equation*}
        |\Ord(X)| = n!
      \end{equation*}
  \end{itemize}
  So we know that $\Sym$ and $\Ord$ have exactly the same number of elements
  and we can come up with a mapping between those elements, such that $\Sym(X)
  \iso \Ord(X)$ for all $X \in \cat{B}$. However, we have also shown that we
  cannot define a natural transformation $\Sym \to \Ord$ which gives that
  there's no natural isomorphism between those categories.
\end{answer}

@@

                    Let $A, A' \in \cat{A}$ and $g \from F(A) \to F(A')$.
                    We define $f := \eta_{A'}^{-1} \circ G(g) \circ \eta_A$ and use the naturality axiom for $\eta$ in order to get:
                        G(F(f)) & = \eta_A' \circ f \circ \eta_A^{-1}\\
                                & = \eta_A' \circ \eta_{A'}^{-1} \circ G(g) \circ \eta_A \circ \eta_A^{-1}\\
                                & = G(g)
                    Since $G$ is faithful we obtain $F(f) = g$.
                    Thus $F$ is full.
